\documentclass[11pt]{article} 

\usepackage[margin=0.7in]{geometry}
\usepackage{nopageno}
\setlength\parindent{0pt}

\begin{document}

\begin{center}
    John Smith \\
    707 Pelton Avenue \\
    Santa Cruz, CA 95060 \\
    (123) 456-7890 \\
\end{center} \\

April 19, 2019 \\

\vspace{.3em}

Hiring Manager 

Thermo Fisher Scientific 

5823 Newton Drive 

Carlsbad, CA 92008 \\

\vspace{.3em}

Dear Hiring Manager, \\

I'm a senior undergraduate student at the University of California, Santa Cruz and am planning to graduate in June of this year with a B.S. in Computer Science. I'm seeking to begin my career in my hometown of San Diego and your job opening for a Data Engineer \& Business Intelligence role piqued my interest as it looks like a unique blend of data science, computer science, and business partnership--three areas that map perfectly to my interests \& skillset.\\

I believe I would be a great fit for this opening on your team for three reasons:
\begin{enumerate}
    \item \textbf{Strong background in programming \& databases } | I have a well-rounded programming background in a number of languages and platforms, including SQL, Python, and React Native, and I learn new languages quickly. I also have a strong interest and skillset in complex database systems, including distributed systems, thanks to my coursework and projects at UCSC. Of all my classes, I've most enjoyed working with databases as they present the interesting challenge of creating order and meaning from chaos.
    \item \textbf{Scrum \& tech writing experience} | I have extensive experience creating clear, concise documentation for apps and projects--as a Research Assistant, I created a detailed document describing how to set up a new prototype ARM server for an enterprise data center. I also enjoy organizing a team towards a common goal, which I did as Scrum Master for a mobile app called Civic Duty. As part of this team, I was responsible for presenting our demos to leadership and working with them to evaluate what features to add to the app, then coordinating with our front-end and back-end developers to deliver those features according to schedule.
    \item \textbf{My communication \& leadership skills} | In my classes, my favorite roles have been team leader and Scrum Master. I've found that I have a unique ability in being able to describe complex technical concepts in easy-to-understand terms to a non-technical audience. I also love collaborating as part of cross-functional teams--my experience as a Research Assistant working with Stanford students \& faculty as well as employees at a tech hardware company was incredibly fulfilling as we worked together towards a common goal.
\end{enumerate} \\

\vspace{.3em}


I see Thermo Fisher Scientific as a place where I hope to make significant contributions and establish a long-term career. I believe my accomplishments at UCSC and passion for data analytics will help me to hit the ground running and deliver results quickly. I would love to meet with you to discuss how I can help Thermo Fisher tackle business issues and continue to drive insights and innovation. Thank you for your time and consideration. \\

\vspace{.3em}


\hfill Sincerely,

\hfill John Smith\\


\end{document}