% LaTeX file for resume 
% This file uses the resume document class (res.cls)
% Used a resume template provided by the Rensselaer Polytechnic Institute as a starting guideline.

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
%\textwidth=5.2in % increase textwidth to get smaller right margin
\oddsidemargin -.3in
\evensidemargin -.3in
\textwidth=5.5in
\textheight=10.3in
\itemsep=-0.3in
\parsep=-0.3in

\begin{document} 
 
\name{John Smith\\[18pt]}
 
\address{{\bf Address} \\ 707 Pelton Avenue \\ Santa Cruz, CA 95060}
\address{{\bf Mobile:} (858) 123-4567 \\ {\bf Email:} johnsmith@ucsc.edu \\ {\bf Github:} johnsmith}

 
\begin{resume}
 
\section{Objective} 
Well-rounded and team-oriented Computer Science graduate seeking a software engineer or a database administrator role in the biotech or tech industries within the San Diego area.

\section{Education} 
{\bf Bachelor of Science in Computer Science} \hfill September 2017 - June 2019 \\
University of California, Santa Cruz \\
3.34 GPA

{\bf Associate of Science in Mathematics} \hfill August 2015 - May 2017 \\
{\bf Associate of Arts in Communication} \\
San Diego City College \\
3.4 GPA

\section{Experience}
 {\bf Undergraduate Research Assistant} \hfill Summer 2018 \\
 Department of Computer Engineering; Advisor: Prof. Heiner Litz \\
 University of California, Santa Cruz \\
 \begin{itemize} \itemsep -1pt 
 \item Collaborated closely with Prof. Litz and a fellow student to significantly improve the remote access speed to NVMe Flash in an enterprise data center and reduce the data center's power consumption. 
 \item Set up and maintained a headless Ubuntu server, using custom kernels on a new prototype ARMv8-A system.
 \item Worked with a research team at Stanford University and a large computer hardware company in the Silicon Valley to set up the server; handled and relayed protected intellectual property securely.
 \item Created detailed documentation describing server set-up, maintenance, troubleshooting, and next steps for continuing the research and adding more functionality to the server.
 \end{itemize}
 
\section{Selected\\Project}
{\bf Civic Duty} \hfill Summer 2018 \\
University of California, Santa Cruz \\
\begin{itemize} \itemsep -1pt 
\item Worked as part of a 5-person team to design and develop a voter information mobile app on iOS and Android operating systems in 5 weeks using React Native, Python, and Adobe XD.
\item Acted as Scrum Master and facilitated daily scrums, planning poker sessions, product demos, sprint retrospectives, and burndown charts. Presented demos and new product features to faculty and staff.
\end{itemize}

\section{Skills}
Java $\cdot$ Python $\cdot$ C $\cdot$ C++ $\cdot$ Haskell $\cdot$ SQL $\cdot$ Matlab $\cdot$ React Native $\cdot$ JavaScript $\cdot$ HTML $\cdot$ CSS $\cdot$ \LaTeX $\cdot$ Agile $\cdot$ Scrum $\cdot$ Unix $\cdot$ Git
 
\section{Coursework}
 Distributed Systems $\cdot$ Operating Systems $\cdot$ Database Systems $\cdot$ Algorithm Analysis $\cdot$ Computer Architecture $\cdot$ Software Engineering $\cdot$ Computational Methods $\cdot$ Comparative Programming Languages $\cdot$ Abstract Data Types $\cdot$ Web Applications $\cdot$ Technical Writing $\cdot$ Probability Theory $\cdot$ Intermediate German

\section{Extracurricular}
Member of the Association for Computing Machinery \\
Team leader and administrator of the 2018 UCSC Dota 2 esports team \\

\textit{Note: This r\'esum\'e used a template from the Rensselaer Polytechnic Institute as a starting guideline.}


\end{resume} 
\end{document} 



