\documentclass[11pt]{article} 

\usepackage[margin=1in]{geometry}
\usepackage{nopageno}

\begin{document}

\begin{center}
    \huge Statement of Purpose \\
    \huge for a MS in Computer Science at the University of California, Santa Cruz \\
    
    \vspace{.75em}
    
    \Large John Smith
\end{center}

Ever since I was young, when other kids were dreaming of being astronauts and sports stars, I knew that I wanted to work with computers. I grew up in the 90's, when computers were just starting to take off in the mainstream, and I had an absolute fascination and wonder for just how quickly things moved in the world of computing -- it seemed like every year, bigger and better technology was being released. I was fortunate to have my uncle, the only computer hobbyist in my family at the time, recognize my shared interest in computing. He struck a deal with me: he would give me some old parts laying around his office for me to build a computer, but only on the condition that I had to build it myself, with as little guidance from him as possible. How could I refuse? All these years later, as an adult, that feeling and sense of amazement with computers is still just the same. I'm fortunate to have been able to study and learn in the field that I love.\\

The University of California, Santa Cruz was one of my dream schools when I was applying for undergraduate programs for Computer Science, and it remains one of my dream schools as I'm applying for Master's programs. The quality of education that I received as an undergraduate, from some of the top researchers in the world, is an experience that could be replicated at very few other schools. Some of the most impactful courses for me were Database Systems with Shel Finkelstein, where I learned that I loved SQL and working with databases, and Algorithm Analysis with Dimitris Achlioptas, which exponentially strengthened my logical thinking and programming ability. I was fortunate enough to even take part in a research lab with Heiner Litz, which was very exciting for me and further introduced me to the unique blend of industry and academia that UC Santa Cruz provides.\\

I would like to join UC Santa Cruz's Data Center Computing or Databases program. While I'm interested in nearly all aspects of computer science, those two programs pique my interest the most, and are most closely related to what I've specialized in throughout my education thus far. I want to further strengthen my involvement in and understanding of the important world of databases as we move increasingly towards a world of cloud computing. \\

Looking towards the future and my long-term goals, I plan to enter industry after earning my Master's degree. Although I greatly enjoy academia, I want to experience working for a mid-size or large tech company before deciding if I want to pursue a PhD. Whether I'm in industry or academia, I am certain that I want to continue the pursuit of knowledge in the beautiful, complex field of computer science.\\
\end{document}